Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos

### 2014-05-08 paper/main.tex
minor typos fixed

In the last decade new algorithms have implemented cosmic web
classifications that go beyond the local density by defining a
location to be a peak, sheet, filament or void depending on the
symmetry properties of the local dark matter distribution. With the
aid of simulations it has been established that halos of a given mass
form earlier in denser regions; concentration, angular momentum and
shape can also be aligned with these web
elements. \citep[e.g][]{AragonCalvo2007,Hahn2007,,Zhang2009,Gonzalez2010,Noh2011,Codis2012,Libeskind2013,Trowland2013}.

@@

\end{tabular}\\
\caption{Shape alignment with the cosmic web, 
$\hat{e}_1$ ($\hat{e}_3$)
is the major (minor) eigenvector of
the corresponding shear. 
Summary of theoretical
  results provided by methods similar to ours.}
\end{table*}

@@

\end{tabular}
\caption{Angular momentum alignment with the cosmic web, 
$\hat{e}_1$ ($\hat{e}_3$)
is the major (minor) eigenvector of
the corresponding shear. 
Summary of theoretical
  results provided by methods similar to ours.}

@@

\begin{enumerate}
\item Halos with $(\hat{s}\cdot\hat{e}_1)^2> (\hat{s}\cdot\hat{e}_2)^2$
  and $(\hat{s}\cdot\hat{e}_1)^2> (\hat{s}\cdot\hat{e}_3^2)$, which can
  be considered to aligned mostly along $\hat{e}_1$.
\item Halos with $(\hat{s}\cdot\hat{e}_2)^2> (\hat{s}\cdot\hat{e}_1)^2$
  and $(\hat{s}\cdot\hat{e}_2)^2> (\hat{s}\cdot\hat{e}_3)^2$, which can
  be considered to aligned mostly along $\hat{e}_2$.
\item Halos with $(\hat{s}\cdot\hat{e}_3)^2> (\hat{s}\cdot\hat{e}_1)^2$
  and $(\hat{s}\cdot\hat{e}_3)^2> (\hat{s}\cdot\hat{e}_2)^2$, which can
  be considered to aligned mostly along $\hat{e}_3$.
\end{enumerate}

>>>>

In the last decade new algorithms have implemented cosmic web
classifications that go beyond the local density by defining a
location to be a peak, sheet, filament or void depending on the
symmetry properties of the local dark matter distribution. With the
aid of simulations it has been established that halos of a given mass
form earlier in denser regions; concentration, angular momentum and
shape can also be aligned with these web
elements. \citep[e.g][]{AragonCalvo2007,Hahn2007,Zhang2009,Gonzalez2010,Noh2011,Codis2012,Libeskind2013,Trowland2013}.

@@

\end{tabular}\\
\caption{Shape alignment with the cosmic web, 
$\hat{e}_1$ ($\hat{e}_3$)
is the major (minor) eigenvector of
the corresponding tensor. 
Summary of theoretical
  results provided by methods similar to ours.}
\end{table*}

@@

\end{tabular}
\caption{Angular momentum alignment with the cosmic web, 
$\hat{e}_1$ ($\hat{e}_3$)
is the major (minor) eigenvector of
the corresponding tensor. 
Summary of theoretical
  results provided by methods similar to ours.}

@@

\begin{enumerate}
\item Halos with $(\hat{s}\cdot\hat{e}_1)^2> (\hat{s}\cdot\hat{e}_2)^2$
  and $(\hat{s}\cdot\hat{e}_1)^2> (\hat{s}\cdot\hat{e}_3)^2$, which can
  be considered to aligned mostly along $\hat{e}_1$.
\item Halos with $(\hat{s}\cdot\hat{e}_2)^2> (\hat{s}\cdot\hat{e}_1)^2$
  and $(\hat{s}\cdot\hat{e}_2)^2> (\hat{s}\cdot\hat{e}_3)^2$, which can
  be considered to aligned mostly along $\hat{e}_2$.
\item Halos with $(\hat{s}\cdot\hat{e}_3)^2> (\hat{s}\cdot\hat{e}_1)^2$
  and $(\hat{s}\cdot\hat{e}_3)^2> (\hat{s}\cdot\hat{e}_2)^2$, which can
  be considered to aligned mostly along $\hat{e}_3$.
\end{enumerate}
